\documentclass[fontsize=10pt]{tccv}
\usepackage[english]{babel}
\usepackage{graphicx,textcomp}

\begin{document}

\part{CFD Engineer --- Aerodynamicist}{Rafael P\'erez}

\section{Experience \& Projects}

\begin{eventlist}

\workitem{November 2013 -- Present}
     {University of Southampton}
     {Post-Graduate Researcher}

Development of a LES Finite Difference Fortran code for wall bounded flows. Investigate the effect of Leading Edge Modifications on
the performance of thick Aerofoils.
\begin{itemize}
	\itemsep -1pt
	\item Development of High-Performance Parallel CFD code.
	\item Development of High-Quality Multi-Block Structured Grids.
	\item Development of Parallel Post-Processing Tools.
	\item Development of Parallel 3D Interpolation Tools for 
	Grid recycling.
	\item Development of an interactive Python Mesh Generation tool.
\end{itemize}

\workitem{November 2013 -- Present}
	{University of Southampton}
	{Assistant Lecturer}

Lead "Applications of CFD", "CFD Surgery", and "Aerodynamics" modules' lab sessions.
	\begin{itemize}
	\itemsep -1pt
		\item Lead lab sessions for Ansys FLuent \& Star CCM+.
		\item Problem Solving for multiple CFD applications.
		\item Introducing new users to the CFD methodology.
	\end{itemize}

\workitem{September 2012 -- May 2013}
     {University of Southampton}
     {Race Car Design Team}

     Team leader for CFD methodology in a 6-person project whose objective was to design an open wheel Hill Climb Race car.
     \begin{itemize}
	\itemsep -1pt
     	\item Development of a VBA/JAVA code for surrogate modelling optimisation.
     	\item Development of Java macros for automating\\ pre/post processing.
     \end{itemize}

\workitem{September 2011 -- July 2012}
     {University of Madrid}
     {Solar Car Prototype}

Responsible for Aero \& CAD for the desing of a solar powered race car for the \href{http://www.shell.com/global/environment-society/ecomarathon.html}{Shell Eco-Marathon}.
\begin{itemize}
\itemsep -1pt
	\item Responsible for designing the car within competition constraints.
        \item Full Aerodynamic analysis for performance optimisation.
	\item Drag Reduction lead to \textbf{\texttildelow 30\% power savings}.
\end{itemize}
\end{eventlist}


\section{Education}

\begin{eventlist}

\eduitem{2013 -- November 2016 (Expected)}
     	{University of Southampton (UK)}
     	{PhD -- \normalsize{LES of Wavy Leading Edge Aerofoils}} 
	\begin{itemize}
	\itemsep -1pt
		\item Technical Writing
		\item Advaced Computational Methods
		\item Aeroacoustics
	\end{itemize}

\eduitem{2012 -- 2013}
     	{University of Southampton (UK)}
     	{MSc -- Race Car Aerodynamics -- 1:1} 
  	\begin{itemize}
	\itemsep -1pt
	   \item Desing of an Open Wheel Race Car
	   \item CFD Modelling
	   \item Desing Search \& Optimisation
	   \item Wind Tunnel Testing
	\end{itemize}

\eduitem{2007 -- 2012}
	{UPM Madrid (SPAIN)}
	{BEng -- Aeronautical Engineer -- 71\%}
  	\begin{itemize}
	\itemsep -1pt
	   \item Aerodynamics
	   \item Structural Analysis
	   \item Aerospace Maintenance
	\end{itemize}
\end{eventlist}

\section{Communication Skills}

\begin{factlist}
\item{Native}{Spanish, Catalan}
\item{Proficient}{English}
\item{Basic}{French}
\end{factlist}

\section{Software Skills}

\begin{factlist}

\item{Good level}
     {Fortran, Python, Matlab, MPI, OPENMP, Ansys~(Fluent), STAR~CCM+, TecPlot360, Paraview ,CatiaV5, SolidWorks, Office}

\item{Intermediate}
     {Java, \LaTeX, VBA,  Unix, GIT}

\item{Basic level}
     {C++, Pointwise, OpenFoam}

\end{factlist}

\end{document}
