\documentclass[fontsize=10pt]{tccv}
\usepackage[english]{babel}
\usepackage{graphicx,textcomp}
\usepackage{lipsum} 


\begin{document}

\part{CFD/Aeronautical Engineer}{Rafael P\'erez}

\section{Experience \& Projects}
\begin{eventlist}
\eduitem{Nov 2013 -- Feb 2017 $|$ Univ. of Southampton}{}
     {Post-Graduate Researcher}

Investigate the effect of wing shape modifications on
the aerodynamic performance
\begin{itemize}
	\itemsep -2pt
	\item CFD solver \& post-processing tools development (\textbf{Python \& Fortran}) 
	\item High Performance Computing
	\item High Speed Aerodynamics
	\item Compressible flow
	\item High Quality Technical Reports \& Presentations
\end{itemize}

\eduitem{Nov 2013 -- Dec 2016 $|$ Univ. of Southampton}{}
	{Assistant Lecturer}
\begin{itemize}
	\itemsep -2pt
	\item Aerodynamics \& Computational Fluid Dynamics (\textbf{Ansys Fluent \& Star
	CCM+})
	\item Problem Solving/Consulting for multiple CFD applications
	\item Wind Tunnel Testing
\end{itemize}

\eduitem{Nov 2012 $|$ Univ. of Southampton}{}
     {Wind Tunnel Testing}
     \begin{itemize}
	\itemsep -2pt
     	\item Ride-height map measurement
     	\item Front/rear wing angle of attack adjustment
     \end{itemize}

\eduitem{Sep 2012 -- May 2013 $|$ Univ. of Southampton}{}
     {Race Car Design Team}

CFD methodology leader for an open wheel Hill Climb Race car design project
     \begin{itemize}
	\itemsep -2pt
     	\item Obtained \textbf{33\% efficiency} improvement
     	\item CFD workflow automation using Java \& Star-CCM+(\textbf{+500\% productivity})
	\item Cleaning \& Meshing CAD geometry
     \end{itemize}

\eduitem{Sep 2011 -- Jul 2012 $|$ UPM Madrid (Spain)}{}
     {Solar Car Prototype}

Aero \& CAD leader for a
\href{http://www.shell.com/global/environment-society/ecomarathon.html}{Shell
Eco-Marathon} team
\begin{itemize}
\itemsep -2pt
	\item Prototype car modelling (\textbf{CatiaV5})
	\item \textbf{\texttildelow 30\% Drag Reduction} (\textbf{Ansys Fluent})
\end{itemize}
\end{eventlist}

\vspace{-20pt}
\section{Communication Skills}
\begin{factlist}
\item{Native}{Spanish, Catalan}
\item{Proficient}{English}
\item{Basic}{French}
\end{factlist}

\vspace{-20pt}
\section{Software/Computer Skills}
\begin{factlist}
\item{\textbf{Programming:}}
     {Fortran, Python, C++, Java, Unix, Bash, VBA, MATLAB, MPI, OPENMP}
\item{\textbf{Version Control:}}
     {GIT}
\item{\textbf{CAD:}}
     {CatiaV5, SolidWorks}
\item{\textbf{CFD:}}
     {Ansys-Fluent, Star-CCM+, OpenFoam}
\item{\textbf{Mesh/Grid:}}
     {Pointwise, ICEM-CFD, Ansys-Mesh, Gambit}
\item{\textbf{Other:}}
     {MS-Office, MS-Project}
\end{factlist}


\vspace{-20pt}
\section{Education}
\begin{eventlist}
\eduitem{2013 -- 2017 $|$ University of Southampton (UK)}{}
     	{\normalsize{PhD -- CFD \& Aerodynamics}} \\

\vspace{-8pt}
\eduitem{2012 -- 2013 $|$ University of Southampton (UK)}{}
     	{\normalsize{MSc -- Race Car Aerodynamics -- 1:1}} \\

\vspace{-8pt}
\eduitem{2007 -- 2012 $|$ UPM Madrid (SPAIN)}{}
	{\normalsize{BEng -- Aeronautical Engineer -- 2:1 (71\%)}}
\end{eventlist}

\vspace{-25pt}
\section{Publications \& Conferences} 
  	\begin{itemize}
	\itemsep -2pt
\item \textbf{A large-eddy simulation on a deep-stalled aerofoil with a wavy leading edge}. J. Fluid Mech. 813. \href{https://doi.org/10.1017/jfm.2016.841}{doi: 10.1017/jfm.2016.841}.
\item \textbf{Flow characteristics of infinite-span wings with wavy leading edges}. $69^{th}$ APS DFD Meeting, November 2016, Portland (USA). 
\item \textbf{Flow characteristics of deep stalled aerofoils with a wavy
leading edge}. UK Fluids Conference, September 2016, London (UK). 
\item \textbf{Large-eddy simulations of a stalled NACA0021 with a wavy
leading edge}. UKTC Annual Meeting, September 2016, Cambridge (UK).
	\end{itemize}

\vspace{-25pt}
\section{Awards \& Certificates} 
  	\begin{itemize}
	\itemsep -2pt
	\item The Timothy Nickels Prize for best oral presentation on 2016 UKTC Annual Meeting
	\item Star-CCM+ 3 Days Course at London HQ
	\item 300h Catia V5 Course
	\end{itemize}

\vspace{-22pt}
\section{More about me} 
\begin{itemize}
	\itemsep -2pt
	\item Full driving license
	\item Working hours flexibility
	\item Willing to travel
\end{itemize}
\end{document}
