%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Rafael P\'erez-Torr\'o}{April 04, 1989}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:rpereztorro@gmail.com}{rpereztorro@gmail.com}\sbull
+49 1511 7518095\sbull
+34 611 411 155\sbull
\href{https://www.linkedin.com/in/rperezt/}{www.linkedin.com/in/rperezt}
\\
23 Bachwiesen Stra\ss{e}\sbull
70199\sbull
Stuttgart\sbull
Germany

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{SUMMARY}  % a root section title

\vspace{-3pt}  % some vertical spacing
\noindent \emph{Aeronautical engineer with excellent problem-solving skills, 4 years experience using high fidelity CFD, advanced knowledge of CAD software, coding in several programming languages and comfortable in public speech situations.}
\vspace{5pt}  % some vertical spacing
\spacedhrule{0em}{-0.4em}

\roottitle{EXPERIENCE}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.p3-group.com/}{P3-SYSTEMS}}
  {\textsc{Stuttgart, Germany}} {%
  \headedsubsection{TEST ENGINEER}{Sept. 2017 -- Present}
  {\bodytext{P3-Systems is a subsidiary of P3-Group which provides testing services for telematics and electronic systems for the automotive industry since 2006. Based in the Stuttgart's test-house, I am part of the Test-Automation team and provide automatic-test-simulations and defect analysis on a daily basis for multimedia boxes to be installed in Mercedes-Benz cars. \\
  \textbf{Main Duties and highlights:} 
    \begin{itemize}
    	\item Prepare highly-intense testing simulations in order to find hardware and software malfunctions
	\item Analyse simulations and upload newly-found defects to the client's database
	\item CAN bus signal analysis
	\item Agile project management
	\item VisualBasic scripting
	\item Fast-paced working environment
    \end{itemize}
    }}
}

\headedsection
  {\href{https://www.southampton.ac.uk}{UNIVERSITY OF SOUTHAMPTON}}
  {\textsc{Southampton, United Kingdom}} {%
  \headedsubsection
    {POST-GRADUATE RESEARCHER}
    {Nov. 2013 -- Nov. 2017}
    {\bodytext{Investigate the effect of wing shape modifications on the aerodynamic and aeroacoustic performance by means of High-Order Computational Fluid Dynamics (CFD) tools.\\
    \textbf{Main duties and highlights:} 
    \begin{itemize}
    	\item Development of Partial Differential Equation (PDE) solvers using \texttt{Fortran90}
	\item Massive Parallelisation programming with MPI libraries
	\item Development of Structured-grid-generators using \texttt{Fortran90} 
	\item Development of Post-Processing tools in \texttt{Fortran90}, \texttt{Python} and \texttt{Matlab} 
	\item Version Control using GIT
	\item Parallel Post-Processing of large data sets, $\mathcal{O}(TByte)$ 
	\item Stability analysis
	\item Analysis of physical features using BigData tools (Dimensionality Reduction, Dynamic Mode Decomposition, etc.)
	\item Signal analysis in frequency and time domains
	\item High-quality scientific publications (see Publications section below)
	\item Present results in front of large audiences
    \end{itemize}
    }}
  \headedsubsection
    {TEACHING ASSISTANT}
    {Nov. 2013 -- Jan. 2017}
    {\bodytext{Teach Computational Fluid Dynamics, aerodynamics and Wind Tunnel Testing.\\
    \textbf{Main duties and highlights:} 
    \begin{itemize}
	\item Teaching basics of CFD and numerical methods
	\item Leading tutorial sessions for ANSYS-Fluent and Star-CCM+
	\item Leading Wind Tunnel Testing sessions 
	\item Provide CFD advise for final-year-degree projects for students across the engineering spectrum
    \end{itemize}
    }}
}

\spacedhrule{2pt}{2pt}

\roottitle{EDUCATION}

\headedsection
  {\href{https://www.southampton.ac.uk}{University of Southampton}}
  {\textsc{Southampton, United Kingdom}} {%
  \headedsubsection
    {PhD. in Computational Fluid Dynamics \& Aerodynamics}
    {Nov. 2013 -- Nov. 2017}{}}

\headedsection
  {\href{https://www.southampton.ac.uk}{University of Southampton}}
  {\textsc{Southampton, United Kingdom}} {%
  \headedsubsection
    {MSc. in Race Car Aerodynamics}
    {Sep. 2012 -- Sep. 2013}{}}

\headedsection
  {\href{https://www.euita.upm.es}{Universidad Polit\'ecnica de Madrid}}
  {\textsc{Madrid, Spain}} {%
  \headedsubsection
    {BEng. in Aeronautics}
    {Sep. 2007 -- Jun. 2012}{}}

\spacedhrule{20pt}{2pt}

\roottitle{PROJECTS}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.southampton.ac.uk}{UNIVERSITY OF SOUTHAMPTON}}
  {\textsc{Southampton, United Kingdom}} {%
  \headedsubsection{Race Car Design}{Sept. 2012 -- May 2013}
  {\bodytext{Design of an open-wheel race car using \texttt{Star-CCM+} and \texttt{SolidWorks}. The project includes an optimisation procedure which connects \texttt{Matlab}, \texttt{SolidWorks}, and \texttt{Star-CCM+} to perform a fully automated optimisation of the front-wing-element's relative position based on Surrogate Modelling that led to a 30\% improvement of the aerodynamic efficiency.\\
  \textbf{Main Duties and highlights:} 
    \begin{itemize}
	\item 3-D meshing
	\item CFD set-up, post-process and analysis
    	\item Pipe-lining for CAD-CFD-OPTIMISATION interaction using \texttt{VisualBasic}, \texttt{BASH}, and \texttt{Java} scripts
	\item Parametric design using \texttt{SolidWorks} with geometric restrictions
	\item Surrogate modelling using Kriging
	\item Variable space exploration using Latin-Hypercube sampling
	\item 1/2 scale full car wind tunnel testing
    \end{itemize}
    }}
}
\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.euita.upm.es}{UNIVERSIDAD POLIT\'ECNICA DE MADRID}}
  {\textsc{Madrid, Spain}} {%
  \headedsubsection{Solar Car Prototype Design}{Sept. 2011 -- Jun. 2012}
  {\bodytext{Design of a solar car prototype using \texttt{ANSYS-Fluent} and \texttt{CatiaV5} that participated in the \href{http://www.shell.com/energy-and-innovation/shell-ecomarathon.html}{Shell Eco-Marathon}.\\
  \textbf{Main Duties and highlights:} 
    \begin{itemize}
	\item Aerofoil selection for lowest drag
	\item 3-D meshing
	\item CFD set-up, post-process and analysis
	\item Parametric design using \texttt{CatiaV5} with geometric restrictions
	\item Preparation of blueprints for molds production
    \end{itemize}
    }}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{SKILLS}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Programming:}
  {Fortran90, Python, C++, VisualBasic, Bash, Unix, Java, \LaTeX}
\vspace{0.5em}
\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Parallel Programing:}
  {MPI, OpenMP, MPI-IO}
\vspace{0.5em}
\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {CAD:}
  {CatiaV5, SolidWorks}
\vspace{0.5em}
\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {CFD:}
  {ANSYS-Fluent, Star-CCM+, OpenFOAM}
\vspace{0.5em}
\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Meshing:}
  {ANSYS-Mesh, Gambit, PointWise, ICEM-CFD}
\vspace{0.5em}
\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Version Control:}
  {GIT}
\vspace{0.5em}
\inlineheadsection
  {Languages:}
  {Spanish (Mother Tongue), Catalan (Mother Tongue), English (Proficient),\\ French (Basic), German (Very Basic)}
\vspace{0.5em}
\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Other:}
  {Matlab, Matlab-Simulink, MS-Office, Agile (SCRUM), Wind Tunnel Testing}
\vspace{0.5em}

\spacedhrule{1.6em}{-0.4em}

\roottitle{PUBLICATIONS \& CONFERENCES}
\begin{itemize}
\item \textbf{A large-eddy simulation on a deep-stalled aerofoil with a wavy leading edge}. J. Fluid Mech. 813. \href{https://doi.org/10.1017/jfm.2016.841}{doi: 10.1017/jfm.2016.841}.
\item \textbf{Flow characteristics of infinite-span wings with wavy leading edges}. $69^{th}$ APS DFD Meeting, November 2016, Portland (USA). 
\item \textbf{Flow characteristics of deep stalled aerofoils with a wavy
leading edge}. UK Fluids Conference, September 2016, London (UK). 
\item \textbf{Large-eddy simulations of a stalled NACA0021 with a wavy
leading edge}. UKTC Annual Meeting, September 2016, Cambridge (UK).
\item \textbf{Aerodynamics of aerofoils with a wavy
leading edge}. UKTC Annual Meeting, September 2017, London (UK).
\end{itemize}

\spacedhrule{0.0em}{-0.4em}
\roottitle{AWARDS}
\begin{itemize}
	\item The Timothy Nickels Prize for best oral presentation on 2016 UKTC Annual Meeting	
\end{itemize}

\end{document}
